---
title: "Week 14"
output:
  pdf_document: default
  html_notebook: default
---

# R Studio API Code
```{r eval = F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```



# Libraries
```{r message = F}
library(tidyverse)
library(RMariaDB)
library(caret)
```


# Data import and cleaning

## SQL code: sql_tbl
```{r}
con <- dbConnect(MariaDB(),
                 user     = "rnlander_8960r",
                 password = "rTCo.4vQ2vc-",
                 port     = "3306",
                 host     = "tntlab.org",
                 dbname   = "rnlander_8960")

# see all table names in the database
tbl <- dbGetQuery(con, "SELECT * FROM INFORMATION_SCHEMA.TABLES WHERE TABLE_TYPE = 'BASE TABLE'")
# three tables: demos, responses, socialmedia

# check socialmedia table: "code", 
# check responses table: "smu_code", "ident"
# check demos table: "participant_num"
# ident from responses match with participant_num from demos


# join demos and responses by participant number, and join socialmedia by code
sql_tbl <- dbGetQuery(con, 
                      "SELECT * FROM responses 
                      INNER JOIN demos 
                      ON responses.ident = demos.participant_num 
                      LEFT JOIN socialmedia 
                      ON responses.smu_code = socialmedia.code")
```


## Tidyverse: tidy_tbl
```{r}
demos_tbl <- dbGetQuery(con, "SELECT * FROM demos")
sm_tbl <- dbGetQuery(con, "SELECT * FROM socialmedia")
res_tbl <- dbGetQuery(con, "SELECT * FROM responses")

tidy_tbl <- res_tbl %>%
  inner_join(demos_tbl, by = c("ident" = "participant_num")) %>%
  left_join(sm_tbl, by = c("smu_code" = "code"))
```


## Cleaning
```{r}
# mean privacy score, age, and number of social media platforms.
clean_tbl <- tidy_tbl %>%
  # transform variables to numeric
  mutate(rec_events = case_when(rec_events == "NA" ~ NA_integer_,
                                rec_events == "Refused" ~ NA_integer_,
                                rec_events == "Not acceptable at all" ~ 1L,
                                rec_events == "Not very acceptable" ~ 2L,
                                rec_events == "Somewhat acceptable" ~ 3L,
                                rec_events == "Very acceptable" ~ 4L)) %>%
  mutate(rec_products = case_when(rec_products == "NA" ~ NA_integer_,
                                  rec_products == "Refused" ~ NA_integer_,
                                  rec_products == "Not acceptable at all" ~ 1L,
                                  rec_products == "Not very acceptable" ~ 2L,
                                  rec_products == "Somewhat acceptable" ~ 3L,
                                  rec_products == "Very acceptable" ~ 4L)) %>%  
  mutate(rec_friends = case_when(rec_friends == "NA" ~ NA_integer_,
                                 rec_friends == "Refused" ~ NA_integer_,
                                 rec_friends == "Not acceptable at all" ~ 1L,
                                 rec_friends == "Not very acceptable" ~ 2L,
                                 rec_friends == "Somewhat acceptable" ~ 3L,
                                 rec_friends == "Very acceptable" ~ 4L)) %>% 
  mutate(rec_policial = case_when(rec_policial == "NA" ~ NA_integer_,
                                  rec_policial == "Refused" ~ NA_integer_,
                                  rec_policial == "Not acceptable at all" ~ 1L,
                                  rec_policial == "Not very acceptable" ~ 2L,
                                  rec_policial == "Somewhat acceptable" ~ 3L,
                                  rec_policial == "Very acceptable" ~ 4L)) %>%
  mutate(facebook = case_when(facebook == "Facebook" ~ 1L,
                              facebook != "Facebook" ~ 0L),
         twitter = case_when(twitter == "Twitter" ~ 1L,
                             twitter != "Twitter" ~ 0L),
         instagram = case_when(instagram == "Instagram" ~ 1L,
                               instagram != "Instagram" ~ 0L),
         youtube = case_when(youtube == "Youtube" ~ 1L,
                             youtube != "Youtube" ~ 0L),
         snapchat = case_when(snapchat == "Snapchat" ~ 1L,
                              snapchat != "Snapchat" ~ 0L),
         other = case_when(other == "Other" ~ 1L,
                           other != "Other" ~ 0L)) %>%
  # transform age to factor varible
  mutate(age = factor(age)) %>%
  rowwise() %>%
  # mean privacy score (mean_score) and number of social media platforms (smp_num)
  mutate(mean_score = mean(c(rec_events,rec_products, rec_friends,rec_policial), na.rm=T),
         smp_num    = sum(c(facebook, twitter, instagram, other))) %>%
  # select necessary variables for analysis
  select(mean_score, age, smp_num)
           
```


# Analysis
```{r}
lm_mod <- lm(mean_score ~ age*smp_num,
             data = clean_tbl)
summary(lm_mod)
```

# Visualization
```{r}
clean_tbl %>%
  ggplot(aes(x = smp_num, y = mean_score, color = age)) +
  geom_smooth(method = lm, se = FALSE) + 
  theme_classic() + 
  labs(title = "Mean privacy score and Number of social media platforms used by age group", 
       x = "number of social media platforms",
       y = "mean privacy score")
```

# Intepretation

People who used more social medial platforms on average had greater acceptance of privacy intrusions. Older people, compared to younger people, had lower acceptance of privacy intrusions. There is no moderation effect of age on the relationship between social media usage and acceptance of privacy intrusions.
